Attribute fusion in a latent process model for time series of graphs

### 2011-11-13 ssp2011.tex
Submitted to TPAMI

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage{fontenc}
%\usepackage{lmodern}
%\usepackage[utopia]{mathdesign}
\usepackage{graphicx}
\usepackage{xltxtra}
\setmainfont[Mapping=tex-text]{Linux Libertine}
\usepackage[cmex10]{amsmath}
\interdisplaylinepenalty=2500
\usepackage{array}
\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage[tight,normalsize,sf,SF]{subfigure}
\ifCLASSOPTIONcompsoc
\usepackage[font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
\usepackage[font=footnotesize]{subfig}
\fi
\usepackage{subfig}
\usepackage{parskip}
\usepackage{mathrsfs}
\usepackage{bm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\usepackage[colorlinks=true,pagebackref,linkcolor=magenta]{hyperref}
\usepackage[noadjust]{cite}
\renewcommand\arraystretch{1.2}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\newcommand{\argmin}{\operatornamewithlimits{argmin}}
\def\mathllap{\mathpalette\mathllapinternal}
\def\mathllapinternal#1#2{%
\llap{$\mathsurround=0pt#1{#2}$}% $
}
\def\clap#1{\hbox to 0pt{\hss#1\hss}}
\def\mathclap{\mathpalette\mathclapinternal}
\def\mathclapinternal#1#2{%
\clap{$\mathsurround=0pt#1{#2}$}%
}
\def\mathrlap{\mathpalette\mathrlapinternal}
\def\mathrlapinternal#1#2{%
\rlap{$\mathsurround=0pt#1{#2}$}% $
}
\bibliographystyle{IEEEtran}
\begin{document}
\title{Attribute fusion in a latent process model for time series of
  graphs}
\author{Minh~Tang, Youngser~Park, Nam~H.~Lee, and Carey~E.~Priebe%
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem Minh~Tang, Nam~H.~Lee
 and Carey~E.~Priebe are with the Department of Applied Mathematics
 and Statistics, Johns Hopkins University.\protect \\
  Email: \{mtang10, nhlee, cep\}@jhu.edu
\IEEEcompsocthanksitem Youngser Park is with the Center for Imaging
Science , Johns Hopkins University.\protect \\
  Email: youngser@jhu.edu}%
\thanks{}}
\markboth{IEEE Transactions on Pattern Analysis and Machine
  Intelligence (TPAMI)}{}
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
  Hypothesis testing on time series of attributed graphs has
  applications in diverse areas, e.g., social network analysis
  (wherein vertices represent individual actors or organizations),
  connectome inference (wherein vertices are neurons or brain regions)
  and text processing (wherein vertices represent authors or
  documents).  We consider the problem of anomaly/change point
  detection given the latent process model for time series of graphs
  with categorical attributes on the edges presented in \cite{lee11}.
  Various attributed graph invariants are considered, and their power
  for detection as a function of a linear fusion parameter is
  presented.  Our main result is that inferential performance in
  mathematically tractable first-order and second-order approximation
  models does provide guidance for methodological choices applicable
  to the exact (realistic but intractable) model. Furthermore, to the
  extent that the exact model is realistic, we may tentatively
  conclude that approximation model investigations have some bearing
  on real data applications.
\end{abstract}
\begin{IEEEkeywords}
  Anomaly detection, Attributed Random Graphs, Random Dot
  Product Graphs.
\end{IEEEkeywords}}
\maketitle
\section{Introduction}

@@

  $\mathscr{S}$-valued random vectors.

@@

change-point phenomena at time $t = t^{*}$. We chose $\{1,2,\dots,m\}$

@@

  \includegraphics[width=5cm]{graphics/Fig2-SSP2011.pdf}

@@

      \mathbb{E}[Z_v(t)] \equiv \hat{\pi}_0 \\
      \mathrm{Var}[Z_v(t)] \equiv \widehat{\Sigma}_0.

@@

      \mathbb{E}[Z_v(t)] \equiv \hat{\pi}_0, \quad \text{for $v \leq
        m$}  \\
      \mathbb{E}[Z_v(t)] \equiv \hat{\pi}_1, \quad \text{for $v > 
        m$}  \\
      \mathrm{Var}[Z_i(t)] \equiv \widehat{\Sigma}_{0} \quad \text{for $v

@@

      \mathrm{Var}[Z_i(t)] \equiv \widehat{\Sigma}_{1} \quad \text{for $v

@@

  Let $\{G(t)\}$ be a time series of graphs. Let $J_{\lambda}(t)$ be a
  statistic for $G(t)$ of the form as in Eq.~\eqref{eq:6} through
  Eq.~\eqref{eq:3}. We define the running average 
  $\bar{J}^{l}_\lambda(t)$ of $J_{\lambda}$ as
\begin{equation}
  \label{eq:4}
 \bar{J}^{l}_{\lambda}(t) = \frac{1}{l}\sum_{s = 1}^{l} J_{\lambda}(t - s) 
\end{equation}
where $l \in \mathbb{N}$ specified the width of the running-average
window. Our main interest is in the normalized fusion statistic
$T_{\lambda}^{l}(t)$ as depicted in Fig.~\ref{fig:temporal}, namely
\begin{equation}
  \label{eq:7}
 T_{\lambda}^{l}(t) = % \begin{cases}
   % J_{\lambda}(t) - J_{\lambda}(t - 1) & \text{if $m = 1$} \\
   \frac{J_{\lambda}(t) -
     \bar{J}_{\lambda}^{l}(t)}{\sqrt{\tfrac{1}{l-1}
       \sum_{s=1}^{l}(J_{\lambda}(t - s) - \bar{J}_{\lambda}^{l}(t))^2}}
%   & \text{if $m \geq 2$}
 %  \end{cases}
\end{equation}
for $l \geq 2$, i.e., we want to find a parameter $\lambda$ such that
the power of the test using $T_{\lambda}^{l}$ is maximum. We note that
$T_{\lambda}^{l}$ is scale invariant in $\lambda$ for all of our graph
invariants. It was noted in \cite{lee11} that the maximum of the power
for scale invariant tests is attainable in $\{ \lambda \colon \|
\lambda \| = 1 \}$. \\ \\

@@

against $t^{*} = t$ using $T_{\lambda}(t)$ and from these

@@

      \sqrt{\frac{\langle \lambda, \tbinom{n}{2} \eta_{00}

@@

            \lambda \rangle}} T_{\lambda}^{l}(t) & \text{if $t = t^{*}$} \\
      \sqrt{\frac{l}{l + 1}} T_{\lambda}^{l}(t)& \text{if $t <

@@

      \frac{\langle \lambda, \zeta \rangle}{\sqrt{\langle \lambda, \xi \lambda \rangle}} & \text{if $t = t^{*}$} \\
      0 & \text{if $t < t^{*}$}.

@@

      \Bigl(\sqrt{\tfrac{l}{l+1}}\,\Bigr) T_{\lambda}^{l}(t) & \text{if $t <

@@

      \Bigl(\sqrt{\tfrac{l \sigma_0^{2}}{l \sigma_A^{2} + \sigma_0^{2}} }\,\Bigr)

@@

    \mu_0 &= \,\, (m - 1) \langle x, \pi_{11} \rangle + (n-

@@

@@

      - \frac{ \sqrt{\pi}}{6} \gamma & \text{if $t < t^{*}$}

@@

@@

    \frac{\sqrt{\pi}}{6} & \text{if $t < t^{*}$};

@@

$\gamma \approx 0.57721$ is the Euler-Mascheroni constant.

@@

@@

        $t = t^{*}$} \\
      - \tfrac{\sqrt{\pi}}{6} \gamma & \text{if $t < t^{*}$} 

@@

        \tfrac{\sqrt{\pi} b_{n,m}}{6 b_n} & \text{if $t = t^{*}$} \\
        \tfrac{\sqrt{\pi}}{6} & \text{if $t < t^{*}$}.

@@

i.e., $\lambda(k) \not = 0$ for exactly one $k$. Therefore the asymptotic theory

@@

  Hypothesis testing on time series of attributed graphs has
  applications in diverse areas, e.g., social network analysis
  (wherein vertices represent individual actors or organizations), connectome
  inference (wherein vertices are neurons or brain regions) and text
  processing (wherein vertices represent authors or documents). These
  and many other applications may benefit from generalizations of our
  results and the
  model in \cite{lee11} to
  directed, multi, and weighted graphs, as well as the consideration
  of inference with errorful edge attributes through an attribute
  confusion matrix.
  \appendices
\section{Proofs of some stated results}
\label{sec:proofs-some-stated}
\begin{IEEEproof}[Corollary~\ref{cor:1}]
  The maximizer of $\mu_\lambda$ also maximizes
  \begin{equation*}
    \mu_{\lambda}^{2} = \frac{\lambda^{T} \zeta \zeta^{T}
      \lambda}{\lambda^{T} \xi \lambda}
  \end{equation*}
  Because $\xi$ is positive definite, there exists a positive definite matrix
  $\xi^{1/2}$ such that $\xi^{1/2} \xi^{1/2} = \xi$. Letting $\nu = \xi^{1/2}
  \lambda$, the above expression can be rewritten as
  \begin{equation*}
    \mu_{\lambda}^{2} = \frac{\nu^{T} \xi^{-1/2} \zeta \zeta^{T}
      \xi^{-1/2} \nu}{ \nu^{T} \nu}
  \end{equation*}
  The claim then follows directly from the Rayleigh-Ritz theorem for
  Hermitian matrices.
\end{IEEEproof}
\begin{IEEEproof}[Lemma~\ref{lem:3}]
  $\tau_{\lambda}(G)$ is a U-statistics with kernel function
  $h(Y_1, Y_2, Y_3) = Y_1 Y_2 Y_3$. By the theory of U-statistics, we
  know that
  \begin{equation}
    \label{eq:48}
    \frac{\tau_{\lambda}(G) -
      \mathbb{E}[\tau_{\lambda}^{*}(G)]}{\sqrt{\mathrm{Var}[\tau_{\lambda}^{*}(G)]}}
       \overset{\mathrm{d}}{\longrightarrow}  N(0,1)
  \end{equation}
  provided that $\mathrm{Var}[\tau_{\lambda}(G) -
  \tau_{\lambda}^{*}(G)] = o(\mathrm{Var}[\tau_{\lambda}^{*}(G)])$.

  By the independent edge assumption, we have
  \begin{align}
    \mathbb{E}[h(Y_i, Y_j, Y_k) &= \mathbb{E}[Y_i]
  \mathbb{E}[Y_j] \mathbb{E}[Y_k] \\ 
  \mathbb{E}[h(Y_i, Y_j, Y_k) |
  Y_i] &= Y_i \mathbb{E}[Y_j] \mathbb{E}[Y_k].
  \end{align}
 Thus, for $t < t^{*}$, we have $\mathbb{E}[\tau_{\lambda}^{*}(G(t))] = \tbinom{n}{3} \langle
  \lambda, \pi_{00} \rangle^{3}$ and
  \begin{equation}
    \begin{split}
      \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] &=
      \mathrm{Var}\Bigl[\sum_{\{u,v,w\}} Y_{uv} \mathbb{E}[Y_{uw}]
      \mathbb{E}[Y_{vw}]\Bigr] \\
      &= (n-2)^{2} \langle \lambda, \pi_{00} \rangle^{4}
      \mathrm{Var}\Bigl[\sum_{\{u,v\}} Y_{uv} \Bigr] \\
      &= (n-2)^{2} \langle \lambda, \pi_{00} \rangle^{4} \tbinom{n}{2}
      \langle \lambda, \eta_{00} \lambda \rangle.
    \end{split}
  \end{equation}
  We now sketch the derivation of
  $\mathrm{Var}[\tau_{\lambda}^{*}(G(t))]$ for $t = t^{*}$. We partition the set
  $\{u,v\} \in \tbinom{V}{2}$ into the sets 
\begin{gather*}
\mathcal{S}_1 = \{ u,v \in [m]
  \}, \\ \mathcal{S}_2 = \{ u \in [m], v \in [n] \setminus [m]\}, \\
  \mathcal{S}_3 = \{ u, v \in [n] \setminus[m]\}.
\end{gather*} Now, for $\{u,v\} \in \mathcal{S}_1$, we have
\begin{equation}
  \label{eq:58}
  \begin{split}
S_1 Y_{uv} &=\sum_{w \not = u,v} \mathbb{E}[h(Y_{uv}, Y_{uw}, Y_{vw})
\, | \, Y_{uv}] \\
 &= ((m-2) \langle \lambda, \pi_{11} \rangle^{2} + (n-m)
    \langle \lambda, \pi_{10} \rangle^{2})Y_{uv}.
  \end{split}
\end{equation}
The above expression is reasoned as follows. If $w \in [m]$, then
$\mathbb{E}[Y_{uw}] = \mathbb{E}[Y_{vw}] = \langle \lambda,
\pi_{11} \rangle$ and there are $m-2$ possible choices for $w \in [m]$
different from $u$ and $v$. If $w \in [n] \setminus [m]$, then
$\mathbb{E}[Y_{vw}] = \mathbb{E}[Y_{uw}] = \langle \lambda, \pi_{10}
\rangle$ and there are $n - m$ possible choices for $w$. Analogous
reasoning gives the expressions for $S_2$ and $S_3$ in the statement
of the lemma. % We also have
% \begin{equation}
%   \label{eq:56}
%   \mathrm{Var}[Y_{uv}] = \begin{cases}
%     \langle \lambda, \eta_{00} \lambda \rangle & \text{if $\{u,v\} \in
%       \mathcal{S}_1$} \\
%     \langle \lambda, \eta_{01} \lambda \rangle & \text{if $\{u,v\} \in
%       \mathcal{S}_2$} \\
%     \langle \lambda, \eta_{11} \lambda \rangle & \text{if $\{u,v\} \in
%       \mathcal{S}_3$} \\
%     \end{cases}.
% \end{equation}

We therefore have
%  \label{eq:60}
  \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] &= %\mathrm{Var}\Bigl[\sum_{\{u,v,w\}} Y_{uv} \mathbb{E}[Y_{uw}]
      % \mathbb{E}[Y_{vw}]\Bigr] \\ &=
      S_1^{2} \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_1} Y_{uv}] +
      S_2^{2}
      \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_2} Y_{uv}] \\ &+
      S_3^{2}
      \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_3} Y_{uv}]  \\ &=
       \tbinom{m}{2} \langle \lambda, \eta_{00} \lambda \rangle S_1^{2} +
       m(n-m) \langle \lambda, \eta_{01} \lambda \rangle S_2^{2} \\ &+
       \tbinom{n-m}{2} \langle \lambda, \eta_{00} \lambda \rangle S_3^{2}
as desired. To complete the proof one must show that
$\mathrm{Var}[\tau_{\lambda}(G) - \tau_{\lambda}^{*}(G)] =
o(\mathrm{Var}[\tau_{\lambda}^{*}(G)])$ and this follows directly from
the argument in \cite{nowicki88:_subgr_u_statis_method}
or \cite{rukhin09:_asymp_analy_various_statis_random_graph_infer}.
\end{IEEEproof}
\begin{IEEEproof}[Proposition~\ref{prop:3}]
  Let $v \in V(t)$ and denote by $d_{\lambda}(v;t)$ the (fused) degree
  of vertex $v$, i.e.,
    d_{\lambda}(v;t) = \sum_{w \in N(v)} \langle \lambda,
    \Gamma_{vw} \rangle.
  For $t < t^{*}$, each of the $\Gamma_{vw}$ is a multinomial
  trial with probability vector $\pi_{00}$. The following statements are
  made as $n \rightarrow \infty$ for fixed
  $K$.  By the central limit theorem, we have
    \label{eq:17}
    \frac{d_{\lambda}(v;t) - (n-1) \langle \lambda, \pi_{00}
      \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda \rangle}}
    \overset{\mathrm{d}}{\longrightarrow} \mathcal{N}(0, 1).
  We can thus consider the degree sequence of $G(t)$ for $t < t^{*}$
  as a sequence of {\em dependent} normally distributed random
  variables. By an argument analogous to the argument for
  Erd\"{o}s-Renyi random graphs in \cite[\S
  III.1]{bollobas85:_random_graph} we can show that the dependency
  among the $\{d_{\lambda}(v;t)\}_{v \in V(t)}$ can be
  ignored. Another way of doing this is to note that the covariance
  between $X_u$ and $X_v$, where $X_u$ and $X_v$ are the ratio in
  Eq.~\eqref{eq:17} for vertices $u$ and $v$, is given by
    \label{eq:63}
    r = \mathrm{Cov}(X_u,X_v) = 
    \frac{3 \langle \lambda, \pi_{00} \rangle}{\sqrt{(n-1)
        \langle \lambda, \eta_{00} \lambda \rangle}}.
  Because $r \log{n} \rightarrow 0$ as $n \rightarrow \infty$, the
  sample maximum of the $X_u$ converges to the sample maximum of a
  sequence of {\em independent} $\mathcal{N}(0,1)$ random variables.
  $d_{\lambda}(v;t)$, can thus be considered as a sequence
  of independent random variables from a normal distribution. It is
  well known that the sample maximum of standard normal random
  variables converges weakly to a Gumbel distribution \cite[\S
  2.3]{galambos87:_asymp_theor_extrem_order_statis}. It is, however,
  not clear whether the convergence of $\Delta_{\lambda}(t)$ to a

>>>>

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage{fontenc}
\pdfminorversion=4
%\usepackage{lmodern}
\usepackage[utopia]{mathdesign}
\usepackage{graphicx}
%\usepackage{xltxtra}
%\setmainfont[Mapping=tex-text]{Linux Libertine}
\usepackage[cmex10]{amsmath}
\interdisplaylinepenalty=2500
\usepackage{array}
%\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage[tight,normalsize,sf,SF]{subfigure}
\ifCLASSOPTIONcompsoc
\usepackage[font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
\usepackage[font=footnotesize]{subfig}
\fi
\usepackage{subfig}
\usepackage{parskip}
\usepackage{mathrsfs}
\usepackage{bm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\usepackage[colorlinks=true,pagebackref,linkcolor=magenta]{hyperref}
\usepackage[noadjust]{cite}
\renewcommand\arraystretch{1.2}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\newcommand{\argmin}{\operatornamewithlimits{argmin}}
\def\mathllap{\mathpalette\mathllapinternal}
\def\mathllapinternal#1#2{%
\llap{$\mathsurround=0pt#1{#2}$}% $
}
\def\clap#1{\hbox to 0pt{\hss#1\hss}}
\def\mathclap{\mathpalette\mathclapinternal}
\def\mathclapinternal#1#2{%
\clap{$\mathsurround=0pt#1{#2}$}%
}
\def\mathrlap{\mathpalette\mathrlapinternal}
\def\mathrlapinternal#1#2{%
\rlap{$\mathsurround=0pt#1{#2}$}% $
}
\bibliographystyle{IEEEtran}
\begin{document}
\title{Attribute fusion in a latent process model for time series of
  graphs}
\author{Minh~Tang, Youngser~Park, Nam~H.~Lee, and Carey~E.~Priebe%
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem Minh~Tang, Nam~H.~Lee
 and Carey~E.~Priebe are with the Department of Applied Mathematics
 and Statistics, Johns Hopkins University.\protect \\
  Email: \{mtang10, nhlee, cep\}@jhu.edu
\IEEEcompsocthanksitem Youngser Park is with the Center for Imaging
Science , Johns Hopkins University.\protect \\
  Email: youngser@jhu.edu}%
\thanks{}}
\markboth{IEEE Transactions on Pattern Analysis and Machine
  Intelligence (TPAMI)}{}
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
  Hypothesis testing on time series of attributed graphs has
  applications in diverse areas, e.g., social network analysis
  (wherein vertices represent individual actors or organizations),
  connectome inference (wherein vertices are neurons or brain regions)
  and text processing (wherein vertices represent authors or
  documents).  We consider the problem of anomaly/change point
  detection given the latent process model for time series of graphs
  with categorical attributes on the edges presented in \cite{lee11}.
  Various attributed graph invariants are considered, and their power
  for detection as a function of a linear fusion parameter is
  presented.  Our main result is that inferential performance in
  mathematically tractable first-order and second-order approximation
  models does provide guidance for methodological choices applicable
  to the exact (realistic but intractable) model. Furthermore, to the
  extent that the exact model is realistic, we may tentatively
  conclude that approximation model investigations have some bearing
  on real data applications.
\end{abstract}
\begin{IEEEkeywords}
  Anomaly detection, Attributed Random Graphs, Random Dot
  Product Graphs.
\end{IEEEkeywords}}
\maketitle
\section{Introduction}

@@

  independent $\mathscr{S}$-valued random vectors.

@@

change-point phenomena for $(X(t),G(t))$ at time $t = t^{*}$. We chose $\{1,2,\dots,m\}$

@@

  \includegraphics[width=5cm]{graphics/Fig2-SSP2011-hat1.pdf}

@@

      \mathbb{E}[Z_v(t)] \equiv \hat{\pi}_0, \,\, 
  \mathrm{Var}[Z_v(t)] \equiv \widehat{\Sigma}_0 \quad \text{for all
    $v$}.

@@

      \mathbb{E}[Z_v(t)] \equiv \hat{\pi}_1, \,\, 
\mathrm{Var}[Z_v(t)] \equiv \widehat{\Sigma}_{1} \quad \text{for $v

@@

  \mathbb{E}[Z_v(t)] \equiv \hat{\pi}_0, \,\, \mathrm{Var}[Z_v(t)] \equiv \widehat{\Sigma}_{0} \quad \text{for $v

@@

  Let $\{G(t)\}$ be a time series of graphs. Let $J_{\lambda}(t)$ be a
  statistic for $G(t)$ of the form as in Eq.~\eqref{eq:6} through
  Eq.~\eqref{eq:3}. We define the running average 
  $\bar{J}^{l}_\lambda(t)$ of $J_{\lambda}$ as
\begin{equation}
  \label{eq:4}
 \bar{J}^{l}_{\lambda}(t) = \frac{1}{l}\sum_{s = 1}^{l} J_{\lambda}(t - s) 
\end{equation}
where $l \in \mathbb{N}$ specified the width of the running-average
window. Our main interest is in the normalized fusion statistic
$T_{\lambda}^{l}(t)$ as depicted in Fig.~\ref{fig:temporal}, namely
\begin{equation}
  \label{eq:7}
 T_{\lambda}^{l}(t) = % \begin{cases}
   % J_{\lambda}(t) - J_{\lambda}(t - 1) & \text{if $m = 1$} \\
   \frac{J_{\lambda}(t) -
     \bar{J}_{\lambda}^{l}(t)}{\sqrt{\tfrac{1}{l-1}
       \sum_{s=1}^{l}(J_{\lambda}(t - s) - \bar{J}_{\lambda}^{l}(t))^2}}
%   & \text{if $m \geq 2$}
 %  \end{cases}
\end{equation}
for $l \geq 2$, i.e., we want to find a parameter $\lambda$ such that
the power of the test using $T_{\lambda}^{l}$ is maximized. We note that
$T_{\lambda}^{l}$ is scale invariant in $\lambda$ for all of our graph
invariants. It was noted in \cite{lee11} that the maximum of the power
for scale invariant test statistics is attainable in the set $\{ \lambda \colon \|
\lambda \| = 1 \}$. \\ \\

@@

against $t^{*} = t$ using $T_{\lambda}^{l}(t)$ and from these

@@

      \sqrt{\frac{l}{l + 1}} T_{\lambda}^{l}(t)& \text{if $t < t^{*}$}
      \\ \sqrt{\frac{\langle \lambda, \tbinom{n}{2} \eta_{00}

@@

            \lambda \rangle}} T_{\lambda}^{l}(t) & \text{if $t =

@@

      0 & \text{if $t < t^{*}$} \\
      \frac{\langle \lambda, \zeta \rangle}{\sqrt{\langle \lambda, \xi \lambda \rangle}} & \text{if $t = t^{*}$} 

@@

      \sqrt{\tfrac{l}{l+1}}\, T_{\lambda}^{l}(t) & \text{if $t <

@@

      \sqrt{\tfrac{l \sigma_0^{2}}{l \sigma_A^{2} + \sigma_0^{2}} }\,

@@

    \mu_0 &= \,\, (m - 1) \langle \lambda, \pi_{11} \rangle + (n-

@@

      - \frac{ \sqrt{\pi}}{6} \gamma & \text{if $t < t^{*}$} \\

@@

        t^{*}$} 

@@

    \frac{\sqrt{\pi}}{6} & \text{if $t < t^{*}$} \\

@@

@@

where $\gamma \approx 0.57721$ is the Euler-Mascheroni constant.

@@

      - \tfrac{\sqrt{\pi}}{6} \gamma & \text{if $t < t^{*}$} \\

@@

        $t = t^{*}$} 

@@

        \tfrac{\sqrt{\pi}}{6} & \text{if $t < t^{*}$} \\
        \tfrac{\sqrt{\pi} b_{n,m}}{6 b_n} & \text{if $t = t^{*}$}. \\

@@

i.e., $\lambda_k \not = 0$ for exactly one $k$. Therefore the asymptotic theory

@@

Hypothesis testing on time series of attributed graphs has
applications in diverse areas, e.g., social network analysis (wherein
vertices represent individual actors or organizations), connectome
inference (wherein vertices are neurons or brain regions) and text
processing (wherein vertices represent authors or documents). These
and many other applications may benefit from generalizations of our
results and the model in \cite{lee11} to directed, multi, and weighted
graphs, as well as the consideration of inference with errorful edge
attributes through an attribute confusion matrix.
% \appendix[Proofs of some stated results]
% \label{sec:proofs-some-stated}
% \begin{IEEEproof}[Corollary~\ref{cor:1}]
%   The maximizer of $\mu_\lambda$ also maximizes
%   \begin{equation*}
%     \mu_{\lambda}^{2} = \frac{\lambda^{T} \zeta \zeta^{T}
%       \lambda}{\lambda^{T} \xi \lambda}
%   \end{equation*}
%   Because $\xi$ is positive definite, there exists a positive definite matrix
%   $\xi^{1/2}$ such that $\xi^{1/2} \xi^{1/2} = \xi$. Letting $\nu = \xi^{1/2}
%   \lambda$, the above expression can be rewritten as
%   \begin{equation*}
%     \mu_{\lambda}^{2} = \frac{\nu^{T} \xi^{-1/2} \zeta \zeta^{T}
%       \xi^{-1/2} \nu}{ \nu^{T} \nu}
%   \end{equation*}
%   The claim then follows directly from the Rayleigh-Ritz theorem for
%   Hermitian matrices.
% \end{IEEEproof}
% \begin{IEEEproof}[Lemma~\ref{lem:3}]
%   $\tau_{\lambda}(G)$ is a U-statistics with kernel function
%   $h(Y_1, Y_2, Y_3) = Y_1 Y_2 Y_3$. By the theory of U-statistics, we
%   know that
%   \begin{equation}
%     \label{eq:48}
%     \frac{\tau_{\lambda}(G) -
%       \mathbb{E}[\tau_{\lambda}^{*}(G)]}{\sqrt{\mathrm{Var}[\tau_{\lambda}^{*}(G)]}}
%        \overset{\mathrm{d}}{\longrightarrow}  N(0,1)
%   \end{equation}
%   provided that $\mathrm{Var}[\tau_{\lambda}(G) -
%   \tau_{\lambda}^{*}(G)] = o(\mathrm{Var}[\tau_{\lambda}^{*}(G)])$.

%   By the independent edge assumption, we have
%   \begin{align}
%     \mathbb{E}[h(Y_i, Y_j, Y_k) &= \mathbb{E}[Y_i]
%   \mathbb{E}[Y_j] \mathbb{E}[Y_k] \\ 
%   \mathbb{E}[h(Y_i, Y_j, Y_k) |
%   Y_i] &= Y_i \mathbb{E}[Y_j] \mathbb{E}[Y_k].
%   \end{align}
%  Thus, for $t < t^{*}$, we have $\mathbb{E}[\tau_{\lambda}^{*}(G(t))] = \tbinom{n}{3} \langle
%   \lambda, \pi_{00} \rangle^{3}$ and
%   \begin{equation}
%     \begin{split}
%       \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] &=
%       \mathrm{Var}\Bigl[\sum_{\{u,v,w\}} Y_{uv} \mathbb{E}[Y_{uw}]
%       \mathbb{E}[Y_{vw}]\Bigr] \\
%       &= (n-2)^{2} \langle \lambda, \pi_{00} \rangle^{4}
%       \mathrm{Var}\Bigl[\sum_{\{u,v\}} Y_{uv} \Bigr] \\
%       &= (n-2)^{2} \langle \lambda, \pi_{00} \rangle^{4} \tbinom{n}{2}
%       \langle \lambda, \eta_{00} \lambda \rangle.
%     \end{split}
%   \end{equation}
%   We now sketch the derivation of
%   $\mathrm{Var}[\tau_{\lambda}^{*}(G(t))]$ for $t = t^{*}$. We partition the set
%   $\{u,v\} \in \tbinom{V}{2}$ into the sets 
% \begin{gather*}
% \mathcal{S}_1 = \{ u,v \in [m]
%   \}, \\ \mathcal{S}_2 = \{ u \in [m], v \in [n] \setminus [m]\}, \\
%   \mathcal{S}_3 = \{ u, v \in [n] \setminus[m]\}.
% \end{gather*} 
% We can thus decompose $\mathrm{Var}[\tau_{\lambda}^{*}(G(t))]$ as 
% \begin{equation}
%   \begin{split}
%   \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] &= S_1^{2} \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_1} Y_{uv}] +
%   S_2^{2}
%   \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_2} Y_{uv}] \\ &+
%   S_3^{2}
%   \mathrm{Var}[\sum_{\{u,v\} \in \mathcal{S}_3} Y_{uv}] 
%   \end{split}
% \end{equation}
% Now, for $\{u,v\} \in \mathcal{S}_1$, we have
% \begin{equation}
%   \label{eq:58}
%   \begin{split}
% S_1 Y_{uv} &=\sum_{w \not = u,v} \mathbb{E}[h(Y_{uv}, Y_{uw}, Y_{vw})
% \, | \, Y_{uv}] \\
%  &= ((m-2) \langle \lambda, \pi_{11} \rangle^{2} + (n-m)
%     \langle \lambda, \pi_{10} \rangle^{2})Y_{uv}.
%   \end{split}
% \end{equation}
% The above expression is reasoned as follows. If $w \in [m]$, then
% $\mathbb{E}[Y_{uw}] = \mathbb{E}[Y_{vw}] = \langle \lambda,
% \pi_{11} \rangle$ and there are $m-2$ possible choices for $w \in [m]$
% different from $u$ and $v$. If $w \in [n] \setminus [m]$, then
% $\mathbb{E}[Y_{vw}] = \mathbb{E}[Y_{uw}] = \langle \lambda, \pi_{10}
% \rangle$ and there are $n - m$ possible choices for $w$. Analogous
% reasoning gives the expressions for $S_2$ and $S_3$ in the statement
% of the lemma.

% We also have
%  \begin{equation}
%    \label{eq:56}
%    \mathrm{Var}[Y_{uv}] = \begin{cases}
%      \langle \lambda, \eta_{00} \lambda \rangle & \text{if $\{u,v\} \in
%        \mathcal{S}_1$} \\
%      \langle \lambda, \eta_{01} \lambda \rangle & \text{if $\{u,v\} \in
%        \mathcal{S}_2$} \\
%      \langle \lambda, \eta_{11} \lambda \rangle & \text{if $\{u,v\} \in
%        \mathcal{S}_3$} \\
%      \end{cases}.
%  \end{equation}
% and thus
% \begin{equation*}
%   \begin{split}
%     \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] &=
%     \tbinom{m}{2} \langle \lambda, \eta_{00} \lambda \rangle S_1^{2} +
%     m(n-m) \langle \lambda, \eta_{01} \lambda \rangle S_2^{2} \\ &+
%     \tbinom{n-m}{2} \langle \lambda, \eta_{00} \lambda \rangle S_3^{2}
%   \end{split}
% \end{equation*}
% as desired. To complete the proof one must show that
% $\mathrm{Var}[\tau_{\lambda}(G) - \tau_{\lambda}^{*}(G)] =
% o(\mathrm{Var}[\tau_{\lambda}^{*}(G)])$ and this follows directly from
% the argument in \cite{nowicki88:_subgr_u_statis_method}
% or \cite{rukhin09:_asymp_analy_various_statis_random_graph_infer}.
% \end{IEEEproof}
% \begin{IEEEproof}[Proposition~\ref{prop:3}]
%   Let $v \in V(t)$ and denote by $d_{\lambda}(v;t)$ the (fused) degree
%   of vertex $v$, i.e.,
%   \begin{equation*}
%     d_{\lambda}(v;t) = \sum_{w \in N(v)} \langle \lambda,
%     \Gamma_{vw} \rangle.
%   \end{equation*}
%   For $t < t^{*}$, each of the $\Gamma_{vw}$ is a multinomial
%   trial with probability vector $\pi_{00}$. The following statements are
%   made as $n \rightarrow \infty$ for fixed
%   $K$.  By the central limit theorem, we have
%   \begin{equation}
%     \label{eq:17}
%     \frac{d_{\lambda}(v;t) - (n-1) \langle \lambda, \pi_{00}
%       \rangle}{\sqrt{(n-1) \langle \lambda, \eta_{00} \lambda \rangle}}
%     \overset{\mathrm{d}}{\longrightarrow} \mathcal{N}(0, 1).
%   \end{equation}
%   We can thus consider the degree sequence of $G(t)$ for $t < t^{*}$
%   as a sequence of {\em dependent} normally distributed random
%   variables. By an argument analogous to the argument for
%   Erd\"{o}s-Renyi random graphs in \cite[\S
%   III.1]{bollobas85:_random_graph} we can show that the dependency
%   among the $\{d_{\lambda}(v;t)\}_{v \in V(t)}$ can be
%   ignored. Another way of doing this is to note that the covariance
%   between $X_u$ and $X_v$, where $X_u$ and $X_v$ are the ratio in
%   Eq.~\eqref{eq:17} for vertices $u$ and $v$, is given by
%   \begin{equation}
%     \label{eq:63}
%     r = \mathrm{Cov}(X_u,X_v) = 
%     \frac{3 \langle \lambda, \pi_{00} \rangle}{\sqrt{(n-1)
%         \langle \lambda, \eta_{00} \lambda \rangle}}.
%   \end{equation}
%   Because $r \log{n} \rightarrow 0$ as $n \rightarrow \infty$, the
%   sample maximum of the $X_u$ converges to the sample maximum of a
